Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increases Repair Time?

### 2015-02-23 phaseDelay.tex
Updates from ShareLaTeX

\documentclass{sig-alternate}
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}} 
\newcommand{\lucas}[1]{\textcolor{red}{#1}} 
\newcommand{\bill}[1]{\textcolor{blue}{#1}} 
\newcommand{\carter}[1]{\textcolor{cyan}{#1}} 
%\newenvironment{changed}{\par}{\par}

@@

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Exponentially Increases  Repair Time?}
\numberofauthors{3}
\author{
\alignauthor
Tim Menzies, \\Carter Pape\\
       \affaddr{CS, NcState, USA}\\
       tim.menzies@gmail.com,\\carterpape@gmail.com
\alignauthor
William Curtis,\\ Forrest Schull\\
\affaddr{SEI, CMU, USA}
wrn,fjshull@sei.cmu.edu
\alignauthor
Lucas \\Layman\\
       \affaddr{Fraunhofer Center,  USA}\\ 
       llayman@fc-md.umd.edu
}

\maketitle
\begin{abstract}
Does
repair time increases exponentially
the longer a defect persists in a system?
This  is very widely belief and the core rational  for
 rejecting   traditional linear development methods
 in favor of more cyclic agile approaches.

@@

\sction{Data}

@@

\begin{figure}
\begin{center}
\scriptsize
\begin{tabular}{rrl}
year& \# issues&\\\hline
2006 &  44 &\\
2007 &  34 &\\
2008&  288 &\rule{1mm}{2mm}\\
2009&  846 &\rule{3mm}{2mm}\\
2010& 1007 &\rule{3mm}{2mm}\\
2011& 3273 &\rule{10mm}{2mm}\\
2012&18102 &\rule{45mm}{2mm}\\
2013&20336 &\rule{50mm}{2mm}\\
2014& 3307 & \rule{10mm}{2mm}\\\cline{1-2}
Total:&47228
\end{tabular}
\end{center}
\caption{This paper studies 47,228 issues recorded 2006 to 2014.}\label{fig:years}
\end{figure}
\begin{figure*}
\begin{center}
\includegraphic[width=6in]{waterfall.png}
\end{center}
\caption{Some parts of the waterfall cycle.}
\end{figure*}
\begin{figure}
\begin{center}
\includegraphic[width=3.5in]{agile.png}
\end{center}
\caption{Some parts of the waterfall cycle.}
\end{figure}

@@

@@

\vspace*{0.5mm}
\scriptsize

\bibliographystyle{unsrt}
\bibliography{refs}

>>>>

\documentclass{sig-alternate}
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{wrapfig}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}} 
\newcommand{\lucas}[1]{\textcolor{red}{#1}} 
\newcommand{\bill}[1]{\textcolor{blue}{#1}} 
\newcommand{\carter}[1]{\textcolor{cyan}{#1}} 
%\newenvironment{changed}{\par}{\par}

@@

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increases  Repair Time?}
\numberofauthors{3}
\author{
\alignauthor
Tim Menzies, \\Carter Pape\\
       \affaddr{CS, NcState, USA}\\
       tim.menzies@gmail.com,\\carterpape@gmail.com
\alignauthor
William Curtis,\\ Forrest Schull\\
\affaddr{SEI, CMU, USA}
wrn,fjshull@sei.cmu.edu
\alignauthor
Lucas \\Layman\\
       \affaddr{Fraunhofer Center,  USA}\\ 
       llayman@fc-md.umd.edu
}

\maketitle
\begin{abstract}
Does
repair time increases dramatically
the longer a defect persists in a system?
This  is very widely belief and the core rational  for
 rejecting   traditional linear development methods
 in favor of more cyclic agile approaches.

@@

\section{Data}

@@

\begin{figure}
\begin{center}
\scriptsize
\begin{tabular}{rrl}
year& \# issues&\\\hline
2006 &  44 &\\
2007 &  34 &\\
2008&  288 &\rule{1mm}{2mm}\\
2009&  846 &\rule{3mm}{2mm}\\
2010& 1007 &\rule{3mm}{2mm}\\
2011& 3273 &\rule{10mm}{2mm}\\
2012&18102 &\rule{45mm}{2mm}\\
2013&20336 &\rule{50mm}{2mm}\\
2014& 3307 & \rule{10mm}{2mm}\\\cline{1-2}
Total:&47228
\end{tabular}
\end{center}
\caption{This paper studies 47,228 issues recorded 2006 to 2014.}\label{fig:years}
\end{figure}
\begin{figure*}[!t]
\begin{center}
\includegraphics[width=6in]{waterfall2.png}
\end{center}
\caption{Different approaches to software development:  waterfall and agile (bottom left).}
\end{figure*}

@@

The data used in this work shirai14

The Team Software ProcessSM (TSPSM) provides a
framework that teams use to collect software process data in real
time, using a defined disciplined process

\begin{figure}
\begin{center}
\scriptsize\begin{tabular}{|l@{~:~}l|}\hline
Bug Prediction Dataset &http://bug.inf.usi.ch \\
Eclipse Bug Data &http://goo.gl/tYKahN \\
FLOSSMetrics& http://flossmetrics.org \\
FLOSSMole &http://flossmole.org \\
IBSBSG& http://www.isbsg.org \\
ohloh& http://www.openhub.net \\
PROMISE &http://promisedata.googlecode.com \\
Qualitas Corpus &http://qualitascorpus.com \\
Software Artifact Repository &http://sir.unl.edu \\
SourceForge Research Data &http://zerlot.cse.nd.edu \\
Sourcerer Project &http://sourcerer.ics.uci.edu \\
Tukutuku &http://www.metriq.biz/tukutuku \\
Ultimate Debian Database &http://udd.debian.org\\\hline
\end{tabular}
\end{center}
\caption{Some repositories of software engineering data.}\label{fig:sedata}
\end{figure}

The TSP couples
the use of integrated product teams with the Personal Software
ProcessSM (PSPSM) to give engineers a defined, planned, and
measured process. For example, PSPSM encourages developers to continually make estimates
about their day-to-day tasks, then compare those estimates against the actual development effort
(in this way, developers can acquire a more realistic understanding of their work behaviour

The Software Engineering Institute (SEI) at
Carnegie Mellon University has collected data from organizations
that have adopted TSP. 
Our efforts focused on data collected by projects that launched
after 2009 and used an automatic data recording tool. 
Data collected included time logs, defect
logs, added and modified size logs, and work
breakdown strcture logs.
The projects
were mostly small to medium, with a median duration of 46 days
and a maximum duration of 90 days. Median team size was 7
people, with a maximum of 40. Hence,  total development 
effort\footnote{
Effort =  duration*teamSize/workDaysPerYear.} for
these projects ranged from 1.3 years (median) to 14.3 years (max).

In these logs
the log records include work start time, work end time, delta
work time, and interruption time. Software engineers are often
interrupted by meetings, requests for technical help, reporting, and
so forth. These events are recorded, in minutes, as interruption
time. In this paper, when we report ``time to resolve an
issue'', we show the difference between the start and end times
of a work session, with any interruption time subtracted (the
difference in times, minus the interruptions).

As of January 2014, the SEI TSP database contained data from 109
TSP projects. The projects started between July 2009 and
September 2013; they included 34 teams and 309 people. Among
the database fact tables, the time store contains 103,023 time logs,
18,408 defect logs, and 7,464 size logs\footnote{\bill{we need to 
update this table}}.

A common property of real-world data sets is the presence
of noisy entries (superfluous  or spurious data). 
The level of noise can be quite high. As reported
in \cite{shepperd12}, around
10\% to 30\%
of the records in the NASA MDP defect data sets are
affected by noise. Nichols et al.~\cite{shirai14}  report that
the noise levesl in the SEI TSE data are smaller than those seen
in other data sets. They found in the SEI TSP data that:\bi 
\item
4\% of the data was incorrect such as  null values of illegal formats;
\item  2\% of the data has inconsistencies such as timestamps
where the stop time was before the start time;
\item 3\% of the data had data that was not credible
such as tasks listed in one day that took like than six hours.
\ei 
That said, certain semantic features of the SEI TSP data should be noted.
Firstly, in the current TSP collection tool, 
fix times are only the developer time for the developer walking through the phased of \fig{waterfall}.
We are currently tracking the fix time for later issues (e.g. those raised during  acceptance test and later
product life cycle). Informally, we can say that in that data we have not detected
a dramatic phase escalation effect (but we have nothing definitive yet to publish  at this time).

\bill{somewhere you have one note on \underline{find} and fix times.  for this paper, we need just fix times. but is there
anything we need to fret about re \underline{find} times?}

\fig{sedata} lists some of the publicly available
software projects data sets currently available to 
SE researchers. Most of the \fig{sedata} data sets have software product information
such as full source code, or summaries of static features.
A subset of that data contain issue or defect reports and/or
the time taken to build these systems. Compared to those data
setss, the SEI TSP data contains much more detailed process details
including a detailed phased breakdown showing what happened at what
phases of the lifecycle. The phased used in this paper are shown in \fig{waterfall}. Note that, in that figure:
\bi 
\item
Several  phases have the same  sub-activities of {\em review} and {\em inspect}\footnote{\bill{plz distinguish review and inspect. does one usually happen first?}}
\item Testing is divided into several statges \footnote{\bill{need a one
line description of test vs qualtest vs inttest vs systemTest vs AcceptTest. I tries some words in the Key to \fig{sedata}. dont know if i got it right.}}
\ei

software-related data sets are available to researchers; well
known examples include those from ISBSG (the International
Software Benchmarking Standards Group) and the Promise Data
Repository. The ISBSG provides datasets from more than 5,600
software development projects and publishes data analysis reports
[11]. The Promise Data Repository mainly stores product metrics
of open source software and NASA projects [17]. For a  list
of other Compared to
other data sets, the TSP database provides a granular level of
development detail that enables not only analysis with great
precision at different levels (e.g., project, team, component, and
individual developer), but also additional opportunity to assess
data quality. We hope to make the TSP database more broadly
available in the future to supplement the other research resources

@@

\clearpage
\vspace*{0.5mm}
\scriptsize
\bibliographystyle{unsrt}
\bibliography{refs}
